Hysteresis in human computation:\\ how one task affects another

### 2014-12-05 docs/publications/2014.09_SCIENCE/man.tex
small change to images.pdf

\paragraph{Experimental setup.}
\begin{figure}
	\centering
	\includegraphics[scale=0.7]{figs/images.pdf}
	\caption{
		Examples of images used for various experiments and treatments:
		A) initial task for \textit{task1:food}, B) initial task for 
		\textit{task1:obj}, C) test task for treatments in \textit{exp1}, 
		D) initial task for \textit{task2:food}, 
		E) initial task for \textit{task2:cult},  
		F) test task for treatments in \textit{exp2}.  
		The full set of experimental materials is shown in the 
		supplementary text.
	}

@@

\subsection*{S7: Analysis of variance}
	\paragraph{Variance in the average fraction food-related labels}
	In the main text, Fig.~\ref{fig:specificity}A shows the difference in 
	the fraction of food related labels used by workers in from different 
	treatments.  The error bars show the 95\% confidence intervals around 
	the estimated difference of means.  It was computed from the
	observed sample standard deviation in the fraction of food labels given
	by individual workers.

	\paragraph{Variance in food vocabulary size.}
	\td{Not sure how to calculate this yet.}

	\paragraph{Variance in food specificity.}
	\td{Need to calculate this using bootstrapping.}

>>>>

\paragraph{Experimental setup.}
\begin{figure}
	\centering
	\includegraphics[scale=0.6]{figs/images.pdf}
	\caption{
		Examples of images used for various experiments and treatments:
		A) initial task for \textit{task1:food}, B) initial task for 
		\textit{task1:obj}, C) test task for treatments in \textit{exp1}, 
		D) initial task for \textit{task2:food}, 
		E) initial task for \textit{task2:cult},  
		F) test task for treatments in \textit{exp2}.  
		The full set of experimental materials is shown in the 
		supplementary text.
	}

@@

\subsection*{S7: Variance and significance tests}

	\paragraph{Variance in the average fraction food-related labels}
	In the main text, Fig.~\ref{fig:specificity}A shows the difference in 
	the fraction of food related labels used by workers in from different 
	treatments.  The error bars show the 95\% confidence intervals around 
	the estimated difference of means.  It was computed from the
	observed sample standard deviation in the fraction of food labels given
	by individual workers.

	\paragraph{Variance in food vocabulary size (lexical richness).}
	The number of unique words in a text is strongly dependant on the size
	of the text: as more text is sampled, previously unseen words continue
	to be found, though at a decreasing rate.  This means that when the 
	lexical richness is measured for a large and small sample, they are not 
	actually estimates of the same quantity.  It is not clear that drawing 
	confidence intervals around the lexical richness measured at one sample 
	size is meaningful, nor is it easily done.

	However, we can construct a null model based on the hypothesis that
	two treatment's have the same probability distribution over tokens
	(and hence the same lexical richness). If treatments $A$ and $B$ have
	the same word frequency distributions, then, they are samples from
	the same population.  Pooling the workers from both treatments together,
	then randomly partitioning them into balanced sets $A'$ and $B'$ will
	still yield samples from the same underlying population.  By repeating 
	this pooling and re-partitioning many times, and computing the 
	relative lexical richness, we can determine the critical difference in
	lexical richness from the 97.5 and 2.5 percentiles.  We can then test 
	the hypothesis that $A$ and $B$ were from the same population by 
	observing whether the difference in lexical richness of the original 
	sets is within this percentile range.

	We performed this calculation using 1000 pooling and resampling 
	iterations, and plotted the 97.5 percentile as a star in 
	Fig~\ref{fig:specificity}B in the main text.  All of the differences
	in lexical richness were significant except that of \textit{frame2}.

	\paragraph{Variance in food specificity.}
	The variance in the specificity measurements was calculated using a 
	bootstrapping proceedure.  For two given treatments $A$ and $B$, 
	119 workers were sampled from each with replacement, giving the bootstrap
	samples $A'$ and $B'$, and the relative specificity between these 
	was measured as described in \textsection S6.
	This was repeated 1000 times.  The 2.5 and 97.5 percentiles were used
	to create the 95\% confidence intervals.
